\chapter{Introduction}
\label{chap:introduction}
This is the manual for the \texttt{ltuthesis} LaTeX template. The template's goal is to provide a headache-free way of integrating the thesis introduction (``Kappa'') and the research papers in one nice-looking, consistent thesis. Even though the template arose from writing composite theses, it can equally well be used for monographs -- see Chapter~\ref{chap:tips_tricks}.

This manual documents the usage of the thesis template with its different bells and whistles providing a complete documentation and guide on how to write your thesis by using this manual. Furthermore, the manual itself is written in the template and can be used as a starting point of your thesis. The source file of this document is filled with lots of comments that explain how the different commands are used.

The template tries to adhere to standard \LaTeX practice and only use techniques that are considered ``the right way'' of doing things in \LaTeX. However, {\color{red} say something blubberish.}

The orgianization of this manual is as follows. Chapter~\ref{chap:usage} highlights the most basic usage of the template and should be read by everyone using this template. Chapter~\ref{chap:tips_tricks} includes some tips and tricks and advanced features of the template, workspace organization, and further topics. In Part II, {\color{red} XX} example research papers are included. Each of the research papers is an example of a paper in the different stages of the academic publishing process.

Finally, {\color{red} a note about warranty and license}.
